Invasive chameleons released from predation display more conspicuous colors

### 2021-12-02 ms.Rmd
Added new analyses to address reviewer comments

>>>>

#########################################################***** NEW
# Background Analysis - Founder           
#########################################################***** NEW
DisplayBgrd <- read.table("./data/Display_5.csv", 
                        header=TRUE, sep=",", dec=".", strip.white=TRUE)
svl_dat <- read.csv("./data/SVL2.csv")

DisplayBgrd <- DisplayBgrd %>% 
                filter(!BodyRegion == "botflank") %>% 
                mutate(Background_pop = ifelse(Background2 == "own", Population, 
                                               if_else(Background2 == "other" & Population == "Hawaii", "Kenya", "Hawaii"))) %>%
                 as.data.frame() #exclude bottom flank.

DisplayBgrd$BodyRegion <- factor(DisplayBgrd$BodyRegion) #updates levels for the variable BodyRegion

DisplayBgrd <- DisplayBgrd %>% 
                mutate(pop_background = interaction(Population, Background_pop)) %>%  
                left_join(select(svl_dat, ID, SVL), by = "ID", keep = FALSE) %>% 
                mutate(sc_svl = scale(SVL, scale = FALSE)) %>% 
                filter(!is.na(SVL))

#unique(DisplayBgrd$pop_background)
###################################
# Male-male display
###################################
##########
# Achromatic Contrast - dL
##########
  # Fit the main effect model
  DispBgrdAC_s6 <- lmer(dL ~ sc_svl  + relevel(pop_background, ref = "Hawaii.Kenya")  + (1|ID), data=DisplayBgrd)
  summary(DispBgrdAC_s6)

  # Check robustness of results to non-independence using Robust Variance Estimator (RVE)
  robust_localAdapt_DispBgrdAC_s6 <- clubSandwich::conf_int(DispBgrdAC_s6, cluster = DisplayBgrd$ID, vcov =  "CR2")

##########
# Chromatic Contrast - dS
##########
    # Fit the main effect model
          DispBgrdCC_s6 <- lmer(dS ~ sc_svl + relevel(pop_background, ref = "Hawaii.Kenya")  + (1|ID), data=DisplayBgrd)
          summary(DispBgrdCC_s6)

    # Check robustness of results to non-indepenedence using Robust Variance Estimator (RVE)
      robust_DispBgrdCC_s6 <- clubSandwich::conf_int(DispBgrdCC_s6, cluster = DisplayBgrd$ID, vcov =  "CR2")

# Filter out only Hawaiian and add in SVL for IDs
CourtshipBgrd <- CourtshipBgrd %>% 
               mutate(pop_background = interaction(Population, Background_pop)) %>%  left_join(select(svl_dat, ID, SVL), by = "ID", keep = FALSE) %>% 
               mutate(sc_svl = scale(SVL, scale = FALSE)) %>% 
                filter(!is.na(SVL))

  # Fit main effects model
    CourtshipAC_s6 <- lmer(dL ~ sc_svl  + relevel(pop_background, ref = "Hawaii.Kenya")  + (1|ID), data=CourtshipBgrd)
    summary(CourtshipAC_s6)

   # Check robustness of results to non-indepenedence using Robust Variance Estimator (RVE)
   robust_CourtshipAC_s6 <- clubSandwich::conf_int(CourtshipAC_s6, cluster = CourtshipBgrd$ID, vcov =  "CR2")

##########
# Chromatic - dS
##########

  # Fit main effect model
      CourtshipCC_s6 <- lmer(dS ~ sc_svl  + relevel(pop_background, ref = "Hawaii.Kenya")  + (1|ID), data=CourtshipBgrd)
      summary(CourtshipCC_s6)

  # Robust variance esatimation to correct SE's for fixed effects given spectral curves are used multiple times for generating JNDs for each individuals data. 
  robust_CourtshipCC_s6 <- clubSandwich::conf_int(CourtshipCC_s6, cluster = CourtshipBgrd$ID, vcov =  "CR2")
